\documentclass[11pt,a4paper]{article}
\begin{document}
\begin{titlepage}
\title{Architectural Requirements}
\author{10353403}
\maketitle
\end{titlepage}

\section{Access Channels}
	\subsection*{Human access channel}
		\begin{itemize}
			\item The system must be accessible via web browsers and web interfaces.
			\item Users must be able to use their mobile devices and desktop to access the system.
			\item The system must accommodate the thick client web based in a sense that the user can perform basic required functionality at client-side without depending on the server.
		\end{itemize}
\section{Quality Requirements}
	\subsection*{Scalability}
	\begin{itemize}
		\item The system must be able to scale to handle more than one loggedin user concurrently.
		\item The system must not restrict the number of threads,posts and comments to be created.
	\end{itemize}
	\subsubsection*{Usability}
	\begin{itemize}
		\item An average user must be ble to use the system without any training.
		\item The system must support multiple languages. It must also support all official languages used in the University.
	\end{itemize}
	\subsubsection*{Security}
	\begin{itemize}
		\item All system functionality is only accessible to users who can be authenticated through the LDAP system.
		\item The system must make certain that only priviledged users(such as lecturers) can create buzz space.
		\item The system must make certain that only registered users on LDAP system can create threads,posts and comments.
	\end{itemize}
	\subsection*{Auditability}
		\begin{itemize}
			\item The system must create a summary of actions that are taken by the users(i.e rating posts,tagging other posts).
			\item The summary should not be editable.
		\end{itemize}
	\subsection*{Integrability}
		\begin{itemize}
			\item The system must be pluggable.
			\item The system must easily integrate with CS LDAP, CS website and Hamster marking system.
		\end{itemize}
		
	\section{Architectural patterns and styles}
\end{document} 

	